Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-26 paper.qmd
Updated data range for the small cluster for MNIST

tsne_minst_scaled_temp <- tsne_minst_scaled |>
  mutate(cluster = if_else((tSNE1 <= 0.92) & (tSNE1 >= 0.75) & (tSNE2 <= 0.62) & (tSNE2 >= 0.44), "small_clust", "big_clust"))

>>>>

tsne_minst_scaled_temp <- tsne_minst_scaled |>
  mutate(cluster = if_else((tSNE1 <= 0.92) & (tSNE1 >= 0.76) & (tSNE2 <= 0.62) & (tSNE2 >= 0.44), "small_clust", "big_clust"))
